\Title

### 2016-03-22 manuscript/manuscript.tex
Fix caption for residuals figure

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-residuals}
    \caption{
        Inversion results for the South American Moho.
        (a) Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
        minus the data predicted by the estimate (a)).
        (b) Differences between the seismological depths of
        \citet{assumpcao2013a} and our gravity-derived Moho depth estimate
        (Fig.~\ref{fig:sam-moho}).
        The inset in b shows a histogram of the differences along with their
        calculated mean and standard deviation (std).
    }
    \label{fig:sam-residuals}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-residuals}
    \caption{
        Residuals for the estimated South American Moho depth in
        Fig.~\ref{fig:sam-moho}.
        (a) Gravity residuals, defined as the difference between the observed data in Fig.~\ref{fig:sam-data}a
        and the data predicted by the estimate in Fig.~\ref{fig:sam-moho}.
        (b) Differences between the seismological depth estimates of
        \citet{assumpcao2013a} and our gravity-derived Moho depth estimate.
        The inset in b shows a histogram of the differences along with their
        calculated mean and standard deviation (std).
        Dotted lines mark the limits of major geologic provinces and
        lithospheric plates.
    }
    \label{fig:sam-residuals}
\end{figure*}
